\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-31 grassposter/2015_EGU_G7_Python/main.tex
increase logo sizes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64951 15284696-431f-4ddb-bdfa-cd5b030d7da7
add TIB logo to posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64959 15284696-431f-4ddb-bdfa-cd5b030d7da7
finish testing box, improve highlights
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64962 15284696-431f-4ddb-bdfa-cd5b030d7da7

\title{
  \begin{minipage}{\textwidth}
    \centering
    Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7
    \bigskip
  \end{minipage}
}
\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
Yann Chemin\inst{2},
Pietro Zambelli\inst{3},
Martin Landa\inst{4},
S\"{o}ren Gebbert\inst{5},
Markus Neteler\inst{6}, and
Peter L\"{o}we\inst{7}
}
\institute{
\large
\instlist{1}North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu),
\instlist{2}International Water Management Institute, Pelawatta, Sri Lanka,
\instlist{3}EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy,
\instlist{4}Faculty of Civil Engineering, Czech Technical University in Prague, Czech Republic,
\instlist{5}Th\"{u}nen Institute of Climate-Smart Agriculture, Braunschweig, Germany,
\instlist{6}Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy,
\instlist{7}German National Library for Science and Technology, Hanover, Germany
}
% \titlegraphic{}

@@

@@

       \newcommand{\logowidth}{0.17\textwidth}
       \newcommand{\logovspace}{\vspace{3ex}}
       \newcommand{\logohspace}{\hspace{1ex}}

       \includegraphics[width=\logowidth]{ncstate}
       \logohspace
       \includegraphics[width=\logowidth]{iwmi}

       \logovspace
       % TODO: TICSA logo (Soeren)
       \includegraphics[width=\logowidth]{ti}
       \logohspace
       \includegraphics[width=\logowidth]{ctu_prague}
       \logohspace
       \includegraphics[width=\logowidth]{eurac}

@@

       \includegraphics[width=\logowidth]{fem_cri}
       \logohspace
       % TODO: GNLST logo (Peter)
       \includegraphics[width=\logowidth]{ncstate}
    \end{minipage}%
    \hfill
   \begin{minipage}{0.74\linewidth}
        \centering
        \color{titlefgcolor}
        {\textcolor{titleTextColor}{\textsf{\textbf{{\fontsize{85}{60}\selectfont \@title}}}}  \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
    \hfill
    \begin{minipage}{0.12\linewidth}
       \centering
       \includegraphics[width=0.35\textwidth]{grass}\\
       \Large \textbf{\textsf{GRASS GIS}}
    \end{minipage}
}
\setlength{\TP@visibletextwidth}{\textwidth-3\TP@innermargin}
\setlength{\TP@visibletextheight}{\textheight-3\TP@innermargin}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Highlights}}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
\item GRASS GIS used directly using Python or GUI or through other software such as QGIS or R.
\item GRASS GIS ecosystem supports code maintenance.
\item The functionality is divided into set of modules (individual tools, functions, algorithms or models).
\item Core libraries and algorithms implemented in C for high performance.
\item The system together with the broad community ensures long term preservation of algorithms.
% \end{itemize}
}

@@

	\bigskip
	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
	\centering
	\includegraphics[width=0.95\linewidth, clip, trim=0 120 0 0]{ipython_nb}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Testing the code}}{
\cite{Petras2014}
}

>>>>

\title{
  \begin{minipage}{\textwidth}
    \centering
    Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7
    \bigskip
  \end{minipage}
}
\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
Yann Chemin\inst{2},
Pietro Zambelli\inst{3},
Martin Landa\inst{4},
S\"{o}ren Gebbert\inst{5},
Markus Neteler\inst{6}, and
Peter L\"{o}we\inst{7}
}
\institute{
\large
\instlist{1}North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu),
\instlist{2}International Water Management Institute, Pelawatta, Sri Lanka,
\instlist{3}EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy,
\instlist{4}Faculty of Civil Engineering, Czech Technical University in Prague, Czech Republic,
\instlist{5}Th\"{u}nen Institute of Climate-Smart Agriculture, Braunschweig, Germany,
\instlist{6}Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy,
\instlist{7}TIB Hannover - German National Library of Science and Technology, Hanover, Germany
}
% \titlegraphic{}

@@

\newlength{\logowidth}

@@

       \setlength{\logowidth}{0.17\textwidth}
       \newcommand{\logovspace}{\vspace{3ex}}
       \newcommand{\logohspace}{\hspace{1ex}}

       \includegraphics[width=1.6\logowidth]{ncstate}
       \logohspace
       \includegraphics[width=\logowidth]{iwmi}

       \logovspace
       \includegraphics[width=2\logowidth]{ti}
       \logohspace
       \includegraphics[width=1.2\logowidth]{ctu_prague}
       \logohspace
       \includegraphics[width=2\logowidth]{eurac}

@@

       \includegraphics[width=1.5\logowidth]{fem_cri}
       \logohspace
       \includegraphics[width=3\logowidth]{tib}
    \end{minipage}%
    \hfill
   \begin{minipage}{0.74\linewidth}
        \centering
        \color{titlefgcolor}
        {\textcolor{titleTextColor}{\textsf{\textbf{{\fontsize{85}{60}\selectfont \@title}}}}  \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
    \hfill
    \begin{minipage}{0.12\linewidth}
       \centering
       \includegraphics[width=0.35\textwidth]{grass}\\
       \Large \textbf{\textsf{GRASS GIS}}
    \end{minipage}
}
\setlength{\TP@visibletextwidth}{\textwidth-3\TP@innermargin}
\setlength{\TP@visibletextheight}{\textheight-3\TP@innermargin}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Highlights}}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS \cite{Neteler2012} is a platform for geospatial computations.
% \item GRASS GIS used directly using Python or GUI or through other software.
\item The functionality is divided into set of modules (individual tools, functions, algorithms or models).
\item Core libraries and algorithms implemented in C for high performance.
\item Python APIs for GRASS GIS are an interface for both the modules and the library.
\item Standardization of inputs and interface serves as a tool for integration a sharing.
\item Other Python tools such as NumPy or IPython can be used together with GRASS GIS.
% \item The system together with the broad community ensures long term preservation of algorithms.
% \item GRASS GIS ecosystem supports code maintenance.
% \end{itemize}
}

@@

	\bigskip
	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
	\centering
	\includegraphics[width=0.95\linewidth, clip, trim=0 145 0 0]{ipython_nb}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Testing the code}}{
% To facilitate the development of the module, GRASS GIS provides
% a Python library for testing (Petras and Gebbert, 2014)
% which helps researchers to ensure the robustness of the
% algorithm, correctness of the results in edge cases
% as well as the detection of changes in results due to new
% development.

To show that all promised functionality is available and algorithm works as expected
every module should be supplied with a test.
This also ensures that functionality
can be simply tested any time in the future \cite{Petras2014}.

\includegraphics[width=\linewidth, clip, trim=0 5 0 0]{gunittest}

% Tests can be written to check the numerical results but also general functionality
% such as if different parameters are accepted.
Tests can use standardize datasets or use custom reference data.
Basic tests can also just look at the statistical summary of a result.
}
